The Hydrogen Epoch of Reionization Array Dish: Characterization with Electromagnetic Simulations

### 2016-01-20 DishSimulations/paper/DishSimulationsPaper_v1.tex
updated simulations draft

\begin{document}
\title{The Hydrogen Epoch of Reionization Array Dish: Characterization with Electromagnetic Simulations}
\author{
Ewall-Wice Aaron\altaffilmark{1,2},
Richard Bradley\altaffilmark{3,4},
Abraham Neben\altaffilmark{1,2},
Nipanjana Patra\altaffilmark{5},
Nithyanandan Thyagarajan \altaffilmark{6},
Jacqueline Hewitt\altaffilmark{1,2},
Zaki S. Ali\altaffilmark{5},
Judd Bowman\altaffilmark{6},
Carina Cheng\altaffilmark{5},
Deboer David\altaffilmark{5},
Parsons Aaron\altaffilmark{5},
Venter Mariet\altaffilmark{7}
and others.
}

@@

\section{Conclusions}
In this paper, we have formally described the impact of instrumental chromaticity on foreground contamination of the 21\,cm signal. We have also used simulations of electromagnetic waves incident from zenith on the primary antenna element on HERA to determine the extent to which reflections and other frequency dependent structure might leak foregrounds into the EoR window. The results of our simulations of the zenith gain of the instrument are broadly consistent with data obtained using reflectometry described in \citep{Patra:2015} and can be summarized in the following points. 
\begin{itemize}
\item The 14-m dish and inverted dipole feed configuration introduces reflections and, as a result, spectral structure, that is in excess of that observed in the antenna design for HERA's predecessor, PAPER. The dish design is intended to greatly increase array collecting area over PAPER without significantly raising the number of correlated elements but we find that in doing so, some degree of spectral smoothness has been sacrificed. Because foreground filtering in delay space cannot distinguish between signal and foregrounds, any regions of $k$-space contaminated by these reflections are effectively unusable in a 21\,cm measurement unless they can be modeled to high fidelity and removed.

>>>>

\begin{document}
\title{The Hydrogen Epoch of Reionization Array Dish: Characterization with Electromagnetic Simulations}
\author{
Ewall-Wice Aaron\altaffilmark{1,2},
Richard Bradley\altaffilmark{3,4},
Abraham Neben\altaffilmark{1,2},
Nipanjana Patra\altaffilmark{5},
Nithyanandan Thyagarajan \altaffilmark{6},
Jacqueline Hewitt\altaffilmark{1,2},
Zaki S. Ali\altaffilmark{5},
Judd Bowman\altaffilmark{6},
Carina Cheng\altaffilmark{5},
David Deboer\altaffilmark{5},
Aaron Parsons\altaffilmark{5},
Mariet Venter\altaffilmark{7}
and others.
}

@@

\section{Conclusions}
In this paper, we have formally described the impact of instrumental chromaticity on foreground contamination of the 21\,cm signal. We have also used simulations of electromagnetic waves incident from zenith on the primary antenna element on HERA to determine the extent to which reflections and other frequency dependent structure might leak foregrounds into the EoR window. The results of our simulations of the zenith gain of the instrument are broadly consistent with data obtained using reflectometry described in \citep{Patra:2015} and can be summarized in the following points. 
\begin{itemize}
\item The 14-m dish and inverted dipole feed configuration introduces reflections and, as a result, spectral structure, that is in excess of that observed in the antenna design for HERA's predecessor, PAPER. The dish design is intended to greatly increase array collecting area over PAPER without significantly raising the number of correlated elements while narrowing the angular field of view and suppressing the overall amplitude of foregrounds but we find that in achieving these ends, some degree of spectral smoothness has been sacrificed. Because foreground filtering in delay space cannot distinguish between signal and foregrounds, any regions of $k$-space contaminated by these reflections are effectively unusable in a 21\,cm measurement unless they can be modeled to high fidelity and removed.
